A Tool for Visualizing Patterns of Spreadsheet Function Combinations

### 2016-04-22 doc/paper.tex
Actually fixing the quotes this time.

	The visualization so far comprises two types of node: the circle \includegraphics{glossary-greenonly}, which
	represents a discrete function in the formula and is size according to its
	frequency relative to the number of times to root function appeared\footnote{The root node, by definition, will
		always be the largest node in a tree.};
	and the numbered squares \includegraphics{glossary-blue}, which represent the positions of arguments within its
	parent function. From this, we can confirm that, of the times it was observed, IF
	can have at most three arguments passed into it, which corresponds with its
	specifications in the
	API.\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2} \par

	Knowing that it is the first argument which contains the conditionals, we click
	on the square labeled "1" to explore. To save space, when more than 10 unique
	arguments have been observed in any position, the tool displays only the first
	ten, with an option to display the rest as the arrow \includegraphics{glossary-arrow}.

@@

	We see that IF contains as its first argument a number of
	comparison operators, such as = and $\le$, and boolean-returning functions, like
	ISNA and AND, with simple equality being the most common and some use as ABS
	being the least seen of everything actually used. \par

	From here, we can further explore the common options among these functions.
	Clicking on the "=" node will yield two arguments
	and expanding each of them will peer into the range of common values of
	equality comparison, which Figure \ref{fig:fullpic} shows. \par

@@

%			\begin{itemize}
%				
%				\item [1] \textbf{Provide an interactive environment for free exploration.}
%				There are a lot of data in some of these collections, and the user should be
%				able to pick for themselves which to explore while ignoring the rest. Furthermore,
%				this exploration should not be designed around answering one specific question
%				but rather be open-ended.
%				
%				\item [!1] \textbf{Do not make judgments about good and bad design.} Though
%				users may certainly approach the tool with the intention of finding particular
%				formulae, \toolname will not prioritize any on metrics of good or bad
%				practice. Rather, it will present them agnostically, referring only to
%				frequency.
%				
%				\item [2] \textbf{Emphasize the quantitative patterns in formula
%					construction.} \toolname should address the questions of how often the
%				spreadsheet programmers used a certain function and where they used it. In
%				this way, it must show precise metrics, such as frequency of use and depth of
%				function nesting, of the dataset it conveys.
%				
%				\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
%				especially, we anticipated some particularly dense trees. Though
%				everything should be accessible in accordance with Goal 1, we should design in
%				a way that reduces noise.
%				
%				\item [3] \textbf{Promote a qualitative understanding of the patterns.}
%				\toolname should supplement its observations with concrete instances of
%				relevant formulae from the corpus. Ideally, it should even direct users to the
%				exact cell in the spreadsheets where the formula was used, contextualizing the
%				functions.
%				
%				\item [!3] \textbf{Do not attempt to explain formulae.} Though \toolname tries
%				to foster understanding by linking pattern to example, it should not provide
%				a precise description of what a complex formula accomplishes. The tool's user
%				must infer this on their own.
%				
%			\end{itemize}

>>>>

	The visualization so far comprises two types of node: the circle
	\includegraphics{glossary-greenonly}, which represents a discrete function in
	the formula and is size according to its frequency relative to the number of
	times to root function appeared\footnote{The root node, by definition, will
		always be the largest node in a tree.}; and the numbered squares
	\includegraphics{glossary-blue}, which represent the positions of arguments
	within its parent function. From this, we can confirm that, of the times it was
	observed, IF can have at most three arguments passed into it, which corresponds
	with its specifications in the
	API\footnote{https://support.office.com/en-us/article/IF-function-69aed7c9-4e8a-4755-a9bc-aa8bbff73be2}. \par

	Knowing that it is the first argument which contains the conditionals, we click
	on the square labeled ``1" to explore. To save space, when more than 10 unique
	arguments have been observed in any position, the tool displays only the first
	ten, with an option to display the rest by clicking the arrow
	\includegraphics{glossary-arrow}.

@@

	We see that IF contains a number of comparison operators as its first argument,
	such as = and $\le$, and boolean-returning functions, like ISNA and AND, with
	simple equality being the most common and some use as ABS being the least seen
	of everything actually used. \par

	From here, we can further explore the common options among these functions.
	Clicking on the ``=" node will yield two arguments and expanding each of them
	will peer into the range of common values of equality comparison, which Figure
	\ref{fig:fullpic} shows. \par

@@

		%			\begin{itemize}
		%
		%				\item [1] \textbf{Provide an interactive environment for free
		% exploration.}
		%				There are a lot of data in some of these collections, and the user should
		% be
		%				able to pick for themselves which to explore while ignoring the rest.
		% Furthermore,
		%				this exploration should not be designed around answering one specific
		% question
		%				but rather be open-ended.
		%
		%				\item [!1] \textbf{Do not make judgments about good and bad design.}
		% Though
		%				users may certainly approach the tool with the intention of finding
		% particular
		%				formulae, \toolname will not prioritize any on metrics of good or bad
		%				practice. Rather, it will present them agnostically, referring only to
		%				frequency.
		%
		%				\item [2] \textbf{Emphasize the quantitative patterns in formula
		%					construction.} \toolname should address the questions of how often the
		%				spreadsheet programmers used a certain function and where they used it.
		% In
		%				this way, it must show precise metrics, such as frequency of use and
		% depth
		% of
		%				function nesting, of the dataset it conveys.
		%
		%				\item [!2] \textbf{Do not overwhelm with numbers.} For popular functions
		%				especially, we anticipated some particularly dense trees. Though
		%				everything should be accessible in accordance with Goal 1, we should
		% design
		% in
		%				a way that reduces noise.
		%
		%				\item [3] \textbf{Promote a qualitative understanding of the patterns.}
		%				\toolname should supplement its observations with concrete instances of
		%				relevant formulae from the corpus. Ideally, it should even direct users
		% to
		% the
		%				exact cell in the spreadsheets where the formula was used,
		% contextualizing
		% the
		%				functions.
		%
		%				\item [!3] \textbf{Do not attempt to explain formulae.} Though \toolname
		% tries
		%				to foster understanding by linking pattern to example, it should not
		% provide
		%				a precise description of what a complex formula accomplishes. The tool's
		% user
		%				must infer this on their own.
		%
		%			\end{itemize}
